\vspace{-1cm} Model linearity breeds contempt: using Bayesian non-linear models to uncover general biogeographical patterns

### 2021-03-09 manuscript/manuscript.tex
Preparing final run

Alternatively, we could have used other distributions that present heavy-tails and fulfil the selection criteria described above. For example, the non-standardized Student's t-distributions is an interesting distribution because, as opposed to the generalized error distribution, it allows for heavy tails without generating a cusp at the center (see Supplementary Fig.~XX). However, we avoided using the non-standardized Student's t-distributions because it does not allow for tails that are lighter than normal (e.g.~$\nu_i>2$ in Eq.~\ref{eq:generalized-response}; Supplementary Fig.~XX), and the sampling of the model is somewhat more challenging (ref).

@@

Maintaining the symmetry of species' distributions, we then allowed the kurtosis---or shape of the tails---of these to vary in different ways. To do so, we changed the response curve of our Bayesian model to follow either a generalized error distribution (Eq.~\ref{eq:generalized-response}) or a non-standardized Student's t-distribution (Eq.~\ref{eq:student-response}). Studying the WAIC values, both non-linear regressions outperformed the baseline model (Supplementary Fig.~XX)\footnote[2]{\label{note1} I am still waiting on the results for this (currently running in the cluster), and this is just my prior expectation based on what I've seen in some of the other models I've been working with.}. In the case of a generalized error distribution, we found the parameter controlling for the kurtosis to be centred around $\nu_i \sim 2$, which corresponds to a distribution with a Gaussian shape (Fig.~\ref{fig:kurtosis-skewness}). Similarly, we found the shape parameter in the non-standardized Student's t-distribution to present large values, also approximating the normal case\footref{note1}. However, in both cases, these parameter estimates displayed a lot of variation between species, which indicates that the shape of the tails of the distribution is species-specific (Supplementary Fig.~XX).

@@

Finally, we studied the skewness of species distributions using the skewed response curve in Eq.~(\ref{eq:skewed-response}). Based on the estimates for the WAIC values and Akaike weights, this model clearly outperformed the rest (Supplementary Fig.~XX), which sheds light on the naturally skewed nature of species' distributions. Studying the mean value of the skewness across species (i.e.~parameter $\hat{\lambda}$), we found that species' distributions showed steeper declines towards lower elevations (Fig.~\ref{fig:kurtosis-skewness}). Moreover, species' physiology seems to strongly shape this parameter, which suggest that distribution skewness is an intrinsic property of species (New Fig.~XX)\footref{note1}.

>>>>

Alternatively, we could have used other distributions that present heavy-tails and fulfil the selection criteria described above. For example, the non-standardized Student's t-distributions is an interesting distribution because, as opposed to the generalized error distribution, it allows for heavy tails without generating a cusp at the center (see Supplementary Fig.~XX). However, we avoided using the non-standardized Student's t-distributions because it does not allow for tails that are lighter than normal (e.g.~$\nu_i>2$ in Eq.~\ref{eq:generalized-response}; Supplementary Fig.~XX), and the sampling of the model can be somewhat more challenging (ref).

@@

Maintaining the symmetry of species' distributions, we then allowed the kurtosis---or shape of the tails---of these to vary in different ways. To do so, we changed the response curve of our Bayesian model to follow a generalized error distribution (Eq.~\ref{eq:generalized-response}). A comparison of the WAIC values showed this non-linear regression to outperform the baseline model (Supplementary Fig.~XX)\footnote[2]{\label{note1} I am still waiting on the results for this (currently running in the cluster), and this is just my prior expectation based on what I've seen in some of the other models I've been working with.}. Studying the resulting posterior distributions, we found the parameter controlling for the kurtosis to be centred around $\nu_i \sim 2$, which corresponds to a distribution with a Gaussian shape (Fig.~\ref{fig:kurtosis-skewness}). However, such parameter estimates displayed a lot of variation across species, which might indicate that the shape of the tails of the distribution is species-specific (Supplementary Fig.~XX).

@@

Next, we studied the skewness of species distributions using the skewed response curve in Eq.~(\ref{eq:skewed-response}). Based on the estimates for the WAIC values and Akaike weights, this model clearly outperformed the rest (Supplementary Fig.~XX), which sheds light on the naturally skewed nature of species' distributions. Studying the mean value of the skewness across species (i.e.~parameter $\hat{\lambda}$), we found that species' distributions showed steeper declines towards lower elevations (Fig.~\ref{fig:kurtosis-skewness}). Moreover, species' physiology seems to strongly shape this parameter, which suggest that distribution skewness is an intrinsic property of species (New Fig.~XX)\footref{note1}.
